\chapter{Literature Review}\label{chap:litreview}

This chapter provides a thorough review of previous research ....

\section{Previous Research}\label{sec:previous}
The study of spatial orientation systems in the Oceanic subgroup of Austronesian languages is well advanced \citep{francois2004,francois2015,palmer2015,bennardo2002,senft2004}. Building on the pioneering work of \citet{adelaar1997}, .... Block quotes can be added with the \verb|quote| environment. 

\begin{quote}
``The question remains whether the above directional terms are used in the same way in Madurese dialects spoken in the northern and north-western parts of Madura, which do not have the sea to the south or the interior to the north. In other words, are the directions still linked to local geography, or have they become independent from it so that the system now has a `fixed' set of terms for cardinal directions?'' \citep[57]{adelaar1997}
\end{quote}


\noindent
It's easy to manage footnotes in \LaTeX. Unlike most word processors, the footnote location and the footnote text are stored together. Just put the footnote text inside the \verb|\footnote{}| command.\footnote{It's good practice to place footnotes immediately following the end of the sentence, even if the reference is only to one word in the sentence. Footnotes following individual words may be justified in interlinear glosses.} 


\section{Second section}
Always good to have a second section. If you somehow find yourself with only one section, then delete that and promote the subsections to sections. 

